---
title: "fearanalysis"
author: "Zack"
date: "6/14/2022"
output: pdf_document
editor_options: 
  chunk_output_type: console
---

```{r}
library(ggplot2)
library(sjPlot)
library(AICcmodavg)
library(tidyverse)
library(dplyr)
library(gridExtra)
library(reshape2)
library(rstatix)
library(ggpubr)
library(gtable)
library(grid)
library(ggeasy)
```

```{r}
dat<- read.csv(file="/Users/explore/Desktop/RAW_meso_data.csv")
head(dat)
```

```{r}
##filtering out each distance so that we can take means and visualize using line graphs 
fc.dat <- dat %>% filter(treatment=="fc")
fc1.dat <- fc.dat %>% filter(distance==1)
fc2.dat <- fc.dat %>% filter(distance==2)
fc3.dat <- fc.dat %>% filter(distance==3)
fc4.dat <- fc.dat %>% filter(distance==4)
fc5.dat <- fc.dat %>% filter(distance==5)


tc.dat <- dat %>% filter(treatment=="tc")
tc1.dat <- tc.dat %>% filter(distance==1)
tc2.dat <- tc.dat %>% filter(distance==2)
tc3.dat <- tc.dat %>% filter(distance==3)
tc4.dat <- tc.dat %>% filter(distance==4)
tc5.dat <- tc.dat %>% filter(distance==5)


on.dat <- dat %>% filter(treatment=="on")
on1.dat <- on.dat %>% filter(distance==1)
on2.dat <- on.dat %>% filter(distance==2)
on3.dat <- on.dat %>% filter(distance==3)
on4.dat <- on.dat %>% filter(distance==4)
on5.dat <- on.dat %>% filter(distance==5)


tw.dat <- dat %>% filter(treatment=="tw")
tw1.dat <- tw.dat %>% filter(distance==1)
tw2.dat <- tw.dat %>% filter(distance==2)
tw3.dat <- tw.dat %>% filter(distance==3)
tw4.dat <- tw.dat %>% filter(distance==4)
tw5.dat <- tw.dat %>% filter(distance==5)


th.dat <- dat %>% filter(treatment=="th")
th1.dat <- th.dat %>% filter(distance==1)
th2.dat <- th.dat %>% filter(distance==2)
th3.dat <- th.dat %>% filter(distance==3)
th4.dat <- th.dat %>% filter(distance==4)
th5.dat <- th.dat %>% filter(distance==5)
```


```{r}
ggplot(data=on.dat, aes(group=hour))+
  geom_boxplot(aes(hour,length, color=as.factor(distance)))+
  facet_wrap(vars(distance))

ggplot(data=tw.dat)+
  geom_boxplot(aes(hour,length, group=hour, color=as.factor(distance)))+
  facet_wrap(vars(distance))

ggplot(data=th.dat)+
  geom_boxplot(aes(hour,length, group=hour, color=as.factor(distance)))+
  facet_wrap(vars(distance))

ggplot(data=tc.dat)+
  geom_boxplot(aes(hour,length, group=hour, color=as.factor(distance)))+
  facet_wrap(vars(distance))

ggplot(data=fc.dat)+
  geom_boxplot(aes(hour,length, group=hour, color=as.factor(distance)))+
  facet_wrap(vars(distance))
```

```{r}
on1<-ggplot(data=on1.dat)+
  geom_point(aes(hour,length))+
  geom_smooth(aes(hour,length))+
  scale_y_continuous(name="Length", limits=c(0, 3.5))+
  theme_bw()

on2<-ggplot(data=on2.dat)+
  geom_point(aes(hour,length))+
  geom_smooth(aes(hour,length))+
  scale_y_continuous(name="Length", limits=c(0, 3.5))+
  theme_bw()

on3<-ggplot(data=on3.dat)+
  geom_point(aes(hour,length))+
  geom_smooth(aes(hour,length))+
  scale_y_continuous(name="Length", limits=c(0, 3.5))+
  theme_bw()

on4<-ggplot(data=on4.dat)+
  geom_point(aes(hour,length))+
  geom_smooth(aes(hour,length))+
  scale_y_continuous(name="Length", limits=c(0, 3.5))+
  theme_bw()

on5<-ggplot(data=on5.dat)+
  geom_point(aes(hour,length))+
  geom_smooth(aes(hour,length))+
  scale_y_continuous(name="Length", limits=c(0, 3.5))+
  theme_bw()
```

```{r}
tw1<- ggplot(data=tw1.dat)+
  geom_point(aes(hour,length))+
  geom_smooth(aes(hour,length))+
  scale_y_continuous(name="Length", limits=c(0, 3.5))+
  theme_bw()

tw2<- ggplot(data=tw2.dat)+
  geom_point(aes(hour,length))+
  geom_smooth(aes(hour,length))+
  scale_y_continuous(name="Length", limits=c(0, 3.5))+
  theme_bw()

tw3<- ggplot(data=tw3.dat)+
  geom_point(aes(hour,length))+
  geom_smooth(aes(hour,length))+
  scale_y_continuous(name="Length", limits=c(0, 3.5))+
  theme_bw()

tw4<- ggplot(data=tw4.dat)+
  geom_point(aes(hour,length))+
  geom_smooth(aes(hour,length))+
  scale_y_continuous(name="Length", limits=c(0, 3.5))+
  theme_bw()

tw5<- ggplot(data=tw5.dat)+
  geom_point(aes(hour,length))+
  geom_smooth(aes(hour,length))+
  scale_y_continuous(name="Length", limits=c(0, 3.5))+
  theme_bw()
```

```{r}
th1<- ggplot(data=th1.dat)+
  geom_point(aes(hour,length))+
  geom_smooth(aes(hour,length))+
  scale_y_continuous(name="Length", limits=c(0, 3.5))+
  theme_bw()

th2<- ggplot(data=th2.dat)+
  geom_point(aes(hour,length))+
  geom_smooth(aes(hour,length))+
  scale_y_continuous(name="Length", limits=c(0, 3.5))+
  theme_bw()

th3<- ggplot(data=th3.dat)+
  geom_point(aes(hour,length))+
  geom_smooth(aes(hour,length))+
  scale_y_continuous(name="Length", limits=c(0, 3.5))+
  theme_bw()

th4<- ggplot(data=th4.dat)+
  geom_point(aes(hour,length))+
  geom_smooth(aes(hour,length))+
  scale_y_continuous(name="Length", limits=c(0, 3.5))+
  theme_bw()

th5<- ggplot(data=th5.dat)+
  geom_point(aes(hour,length))+
  geom_smooth(aes(hour,length))+
  scale_y_continuous(name="Length", limits=c(0, 3.5))+
  theme_bw()
```

```{r}
tc1<- ggplot(data=tc1.dat)+
  geom_point(aes(hour,length))+
  geom_smooth(aes(hour,length))+
  scale_y_continuous(name="Length", limits=c(0, 3.5))+
  theme_bw()

tc2<- ggplot(data=tc2.dat)+
  geom_point(aes(hour,length))+
  geom_smooth(aes(hour,length))+
  scale_y_continuous(name="Length", limits=c(0, 3.5))+
  theme_bw()

tc3<- ggplot(data=tc3.dat)+
  geom_point(aes(hour,length))+
  geom_smooth(aes(hour,length))+
  scale_y_continuous(name="Length", limits=c(0, 3.5))+
  theme_bw()

tc4<- ggplot(data=tc4.dat)+
  geom_point(aes(hour,length))+
  geom_smooth(aes(hour,length))+
  scale_y_continuous(name="Length", limits=c(0, 3.5))+
  theme_bw()

tc5<- ggplot(data=tc5.dat)+
  geom_point(aes(hour,length))+
  geom_smooth(aes(hour,length))+
  scale_y_continuous(name="Length", limits=c(0, 3.5))+
  theme_bw()
```
```{r}
fc1<- ggplot(data=fc1.dat)+
  geom_point(aes(hour,length))+
  geom_smooth(aes(hour,length))+
  scale_y_continuous(name="Length", limits=c(0, 3.5))+
  theme_bw()

fc2<- ggplot(data=fc2.dat)+
  geom_point(aes(hour,length))+
  geom_smooth(aes(hour,length))+
  scale_y_continuous(name="Length", limits=c(0, 3.5))+
  theme_bw()

fc3<- ggplot(data=fc3.dat)+
  geom_point(aes(hour,length))+
  geom_smooth(aes(hour,length))+
  scale_y_continuous(name="Length", limits=c(0, 3.5))+
  theme_bw()

fc4<- ggplot(data=fc4.dat)+
  geom_point(aes(hour,length))+
  geom_smooth(aes(hour,length))+
  scale_y_continuous(name="Length", limits=c(0, 3.5))+
  theme_bw()

fc5<- ggplot(data=fc5.dat)+
  geom_point(aes(hour,length))+
  geom_smooth(aes(hour,length))+
  scale_y_continuous(name="Length", limits=c(0, 3.5))+
  theme_bw()
 
```


```{r}
grid.arrange(on1,tw1,th1,tc1,fc1,on2,tw2,th2,tc2,fc2,on3,tw3,th3,tc3,fc3,on4,tw4,th4,tc4,fc4,on5,tw5,th5,tc5,fc5, nrow=5, ncol=5, top = textGrob("Algal Height vs Time Elapsed", gp = gpar(fontface = "bold", cex = 1.5)),
             bottom = textGrob("Hours Elapsed",gp = gpar(cex = 1.5)))


```
```{r}
grid.arrange(on1, on2,on3,on4,on5,tw1,tw2,tw3,tw4,tw5,th1,th2,th3,th4,th5,tc1,tc2,tc3,tc4,tc5,fc1,fc2,fc3,fc4,fc5, nrow=5, ncol=5, top = textGrob("Algal Height vs Time Elapsed", gp = gpar(fontface = "bold", cex = 1.5)),
             bottom = textGrob("Hours Elapsed",gp = gpar(cex = 1.5)))
```

```{r}
grid.arrange(on1,tw1,th1,tc1,fc1, nrow=1, ncol=5, top = textGrob("Algal Height vs Time Elapsed", gp = gpar(fontface = "bold", cex = 1.5)),
             bottom = textGrob("Hours Elapsed",gp = gpar(cex = 1.5)))
```
```{r}
grid.arrange(on2,tw2,th2,tc2,fc2, nrow=1, ncol=5, top = textGrob("Algal Height vs Time Elapsed", gp = gpar(fontface = "bold", cex = 1.5)),
             bottom = textGrob("Hours Elapsed",gp = gpar(cex = 1.5)))
```
```{r}
grid.arrange(on3,tw3,th3,tc3,fc3, nrow=1, ncol=5, top = textGrob("Algal Height vs Time Elapsed", gp = gpar(fontface = "bold", cex = 1.5)),
             bottom = textGrob("Hours Elapsed",gp = gpar(cex = 1.5)))
```
```{r}
grid.arrange(on4,tw4,th4,tc4,fc4, nrow=1, ncol=5, top = textGrob("Algal Height vs Time Elapsed", gp = gpar(fontface = "bold", cex = 1.5)),
             bottom = textGrob("Hours Elapsed",gp = gpar(cex = 1.5)))
```
```{r}
grid.arrange(on5,tw5,th5,tc5,fc5, nrow=1, ncol=5, top = textGrob("Algal Height vs Time Elapsed", gp = gpar(fontface = "bold", cex = 1.5)),
             bottom = textGrob("Hours Elapsed",gp = gpar(cex = 1.5)))
```




```{r}
```{r}
grid.arrange(on1,on2,on3,on4,on5, nrow=1, ncol=5, top = textGrob("Algal Height vs Time Elapsed", gp = gpar(fontface = "bold", cex = 1.5)),
             bottom = textGrob("Hours Elapsed",gp = gpar(cex = 1.5)))
```
```{r}
grid.arrange(tw1,tw2,tw3,tw4,tw5, nrow=1, ncol=5, top = textGrob("Algal Height vs Time Elapsed", gp = gpar(fontface = "bold", cex = 1.5)),
             bottom = textGrob("Hours Elapsed",gp = gpar(cex = 1.5)))
```
```{r}
grid.arrange(th1,th2,th3,th4,th5, nrow=1, ncol=5, top = textGrob("Algal Height vs Time Elapsed", gp = gpar(fontface = "bold", cex = 1.5)),
             bottom = textGrob("Hours Elapsed",gp = gpar(cex = 1.5)))
```
```{r}
grid.arrange(tc1,tc2,tc3,tc4,tc5, nrow=1, ncol=5, top = textGrob("Algal Height vs Time Elapsed", gp = gpar(fontface = "bold", cex = 1.5)),
             bottom = textGrob("Hours Elapsed",gp = gpar(cex = 1.5)))
```
```{r}
grid.arrange(fc1,fc2,fc3,fc4,fc5, nrow=1, ncol=5, top = textGrob("Algal Height vs Time Elapsed", gp = gpar(fontface = "bold", cex = 1.5)),
             bottom = textGrob("Hours Elapsed",gp = gpar(cex = 1.5)))
```

```


